---
title: 'Élet központi menesztés: lehetõség-elemzés'
author: "Ajánlat Feldlgozó Centrum"
date: '2018 március 20'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
df <- read.csv(here::here("Data", "t_segmented.csv"), stringsAsFactors = FALSE)
```

## Szegmensek összehasonlítása {.columns-2}

```{r, fig.height=4, fig.width=6}
ggplot(
  df %>% gather(MUTATO, ERTEK, DARAB:FTE),
  aes(
    x = IDOSZAK,
    y = ERTEK,
    group = SZEGMENS,
    colour = SZEGMENS
  )
) +
  geom_line() +
  geom_point(shape=15) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(y = "Érték",
       x = "Hónap",
       colour = "Szegmens") +
  facet_grid(MUTATO ~ ., scales = "free")
```

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Data file overview
```{r, echo = TRUE}
str(df)
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3



